Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-25 prop_iop.tex
prop_iop.tex Proof fixed (?)

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{enumerate}
\item \label{enu:sub-event-space-real-quantum2classical}If $\mu':\events'\rightarrow\left[0,1\right]$
is a quantum real-valued probability measure, then there is a classical
real-valued probability measure\nb$\mu:2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu'\left(P\right)=\mu\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}':\events'\rightarrow\mathscr{I}$
is a quantum interval-valued probability measure, then there is a
classical interval-valued probability measure\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}'\left(P\right)=\bar{\mu}\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-real-classical2quantum}If $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
is a classical real-valued probability measure, then $\mu\circ\tau:\widehat{\events}\rightarrow\left[0,1\right]$
is a QRVPM.
\item \label{enu:sub-event-space-Gleason}Given a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$,
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$.
\item $\rho$ in the previous case may not be unique.
\end{enumerate}
\end{thm}

\begin{proof}
\begin{enumerate}
\item Since this case is a special case of the next case, it is sufficient
to prove the next case. 
\item Since $\events'$ is a set of mutually commuting projections, they
can be diagonalized by a common orthonormal basis\nb$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector\nb$P\in\events'$, its eigenvalues are $0$
or $1$. Select its eigenvectors whose eigenvalues are $1$ into a
set\nb$\tau\left(P\right)\subseteq\Omega$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
$\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
By definition\nb\ref{definition:quantum-classical}, $\bar{\mu}'\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
measure by lemma\nb\ref{lemma:classical-probability-measures}.
\item Trivial.
\item If we pick $\rho=\sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\proj{j}$,
then $\rho$ is a density matrix because\nb\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\Tr\left(\proj{j}\right)=1\,.
\end{eqnarray}
Also, 
\begin{eqnarray}
 &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\widehat{\mu}\left(\proj{j}\right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\widehat{\mu}\left(\proj{i}\right)\textrm{ for all }i\,,\\
 &  & \mu_{\rho}^{\mathrm{B}}\left(P_{0}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)\overset{\textrm{IH}}{=}\widehat{\mu}\left(P_{0}\right)+\widehat{\mu}\left(P_{1}\right)=\widehat{\mu}\left(P_{0}+P_{1}\right)
\end{eqnarray}
for orthogonal\nb$P_{0},P_{1}\in\events$. Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$ by induction.
\item Consider a Hilbert space\nb$\Hilb$ of dimension 2, a mutually commuting
sub-event space~$\widehat{\events}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $,
and a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$
such that $\widehat{\mu}\left(\proj{0}\right)=\widehat{\mu}\left(\proj{1}\right)=\frac{1}{2}$.
Then, $\proj{\ps}$ and $\proj{\minus}$ are both density matrices,
and 
\begin{eqnarray*}
 &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{0}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{0}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{0}\right)\,,\\
 &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{1}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{1}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{1}\right)\,.
\end{eqnarray*}
\end{enumerate}
\end{proof}

@@

\begin{proof}By adopting the notation in lemma~\ref{lemma:deterministic-CIVPM},
we have
\begin{equation}
\int X\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu\right\} \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=}\left\{ X\left(\pmeas^{-1}\left(1\right)\right)\cdot1\right\} =\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,.\label{eq:expectation-value-eigenvalue-classical}
\end{equation}
\end{proof}

@@

\begin{lemma}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
and a sequence of random variable~$\left\{ X_{j}\right\} $,
\begin{equation}
\prod_{j}\int X_{j}\rmd\bar{\mu}=\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:Kochen-Specker-Rules-classical}
\end{equation}
\end{lemma}

\begin{proof} 
\begin{equation}
\prod_{j}\int X_{j}\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\prod_{j}\left\{ X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} =\left\{ \prod_{j}X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:expectation-value-eigenvalue-classical-1}
\end{equation}
\end{proof}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}) and its inducing
sub-event space $\events'$, set~$\Omega$, and function~$\tau:\events'\rightarrow2^{\Omega}$.
Then, the random variable~$X:\Omega\rightarrow\mathbb{R}$ defined
by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
is called the random variable induced by $\mathbf{O}$.\end{definition}

@@

\begin{proof}Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\mu}\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one pair
of $\left(s_{0},i_{0}\right)$ such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$.
Therefore, 
\begin{equation}
\expval{\mathbf{O}}_{\mu}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\,.\label{eq:expectation-value-eigenvalue}
\end{equation}
\end{proof}

@@

\begin{lemma}For any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $,
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
\end{lemma}

\begin{proof}Since $\left\{ \mathbf{O}_{j}\right\} $ is a sequence
of commuting observables, they can be diagonalized by a common orthonormal
basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. By lemma~\ref{lemma:QIVPM2QCM},
$\mul$ and $\mur$ are the same cryptodeterministic measure, and
is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $j_{0}$
such that $\mu\left(\proj{j_{0}}\right)=1$. Therefore, by the same
reason as equation~(\ref{eq:expectation-value-eigenvalue}), the
both sides of equation~(\ref{eq:Kochen-Specker-Rules}) are the product
of eigenvalues corresponding to eigenstate~$\ket{j_{0}}$, and should
be equal.\end{proof}

>>>>

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{enumerate}
\item \label{enu:sub-event-space-real-quantum2classical}If $\mu':\events'\rightarrow\left[0,1\right]$
is a quantum real-valued probability measure, then there is a classical
real-valued probability measure\nb$\mu:2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu'\left(P\right)=\mu\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}':\events'\rightarrow\mathscr{I}$
is a quantum interval-valued probability measure, then there is a
classical interval-valued probability measure\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}'\left(P\right)=\bar{\mu}\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-real-classical2quantum}If $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
is a classical real-valued probability measure, then $\mu\circ\tau:\widehat{\events}\rightarrow\left[0,1\right]$
is a QRVPM.
\item \label{enu:sub-event-space-Gleason}Given a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$,
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$.
\item $\rho$ in the previous case may not be unique.
\item The bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ preserves
the following operations.
\begin{itemize}
\item $\tau\left(\mathbb{0}\right)=\emptyset$.
\item $\tau\left(\mathbb{1}\right)=\Omega$.
\item For any projection $P\in\widehat{\events}$, we have $\tau\left(\mathbb{1}-P\right)=\Omega-\tau\left(P\right)$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\widehat{\events}$,
we have $\tau\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\tau\left(P_{i}\right)$.
\end{itemize}
\end{enumerate}
\end{thm}

\begin{proof}
\begin{enumerate}
\item Since this case is a special case of the next case, it is sufficient
to prove the next case. 
\item Since $\events'$ is a set of mutually commuting projections, they
can be diagonalized by a common orthonormal basis\nb$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector\nb$P\in\events'$, its eigenvalues are $0$
or $1$. Select its eigenvectors whose eigenvalues are $1$ into a
set\nb$\tau\left(P\right)\subseteq\Omega$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
$\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
By definition\nb\ref{definition:quantum-classical}, $\bar{\mu}'\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
measure by lemma\nb\ref{lemma:classical-probability-measures}.
\item Trivial.
\item If we pick $\rho=\sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\proj{j}$,
then $\rho$ is a density matrix because\nb\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\Tr\left(\proj{j}\right)=1\,.
\end{eqnarray}
Also, 
\begin{eqnarray}
 &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\widehat{\mu}\left(\proj{j}\right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\widehat{\mu}\left(\proj{i}\right)\textrm{ for all }i\,,\\
 &  & \mu_{\rho}^{\mathrm{B}}\left(P_{0}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)\overset{\textrm{IH}}{=}\widehat{\mu}\left(P_{0}\right)+\widehat{\mu}\left(P_{1}\right)=\widehat{\mu}\left(P_{0}+P_{1}\right)
\end{eqnarray}
for orthogonal\nb$P_{0},P_{1}\in\events$. Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$ by induction.
\item Consider a Hilbert space\nb$\Hilb$ of dimension 2, a mutually commuting
sub-event space~$\widehat{\events}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $,
and a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$
such that $\widehat{\mu}\left(\proj{0}\right)=\widehat{\mu}\left(\proj{1}\right)=\frac{1}{2}$.
Then, $\proj{\ps}$ and $\proj{\minus}$ are both density matrices,
and 
\begin{eqnarray*}
 &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{0}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{0}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{0}\right)\,,\\
 &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{1}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{1}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{1}\right)\,.
\end{eqnarray*}
\item Trivial.
\end{enumerate}
\end{proof}

@@

\begin{proof}By adopting the notation in lemma~\ref{lemma:deterministic-CIVPM},
we have
\begin{eqnarray*}
 &  & \int X\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu\right\} \\
 & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \left\{ X\left(\pmeas^{-1}\left(1\right)\right)\cdot1\right\} =\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,.
\end{eqnarray*}
\end{proof}

@@

\begin{lemma}\label{lemma:deterministic-CIVPM-product}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
and a sequence of random variable~$\left\{ X_{j}\right\} $,
\begin{equation}
\prod_{j}\int X_{j}\rmd\bar{\mu}=\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:Kochen-Specker-Rules-classical}
\end{equation}
\end{lemma}

\begin{proof}
\begin{eqnarray*}
 &  & \prod_{j}\int X_{j}\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\prod_{j}\left\{ X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \\
 & = & \left\{ \prod_{j}X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}\,.
\end{eqnarray*}
\end{proof}

@@

\begin{definition}\label{def:observable2random-variable}Given an
observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition})
and its inducing subspace of events\nb$\events'$, set~$\Omega$,
and function~$\tau:\events'\rightarrow2^{\Omega}$. Then, the random
variable~$X:\Omega\rightarrow\mathbb{R}$ defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
is called the random variable induced by $\mathbf{O}$.\end{definition}

The following lemma shows that .

\begin{lemma}\label{lemma:observable2random-variable}Given an observable~$\mathbf{O}$
with an orthonormal basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$,
$\widehat{\events}=\set{\sum_{\ket{k}\in E}\proj{k}}{E\subseteq\Omega}$,
and the bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$
defined in theorem~\ref{thm:sub-event-space}. By definition~\ref{def:observable2random-variable},
$\mathbf{O}$ induces a random variable\nb$X:\Omega\rightarrow\mathbb{R}$,
if $\mathbf{O}=\sum_{k=0}^{d-1}\lambda_{k}\proj{k}$, then $X=\sum_{k=0}^{d-1}\lambda_{k}\mathbf{1}_{\left\{ \ket{k}\right\} }$.\end{lemma}

\begin{proof}Since $\mathbf{O}$ can be diagonalized by $\Omega$,
each projector in the spectral decomposition\nb$P_{i}^{s}$ is the
summation of some basis vectors\nb$\sum_{k\in S_{i}^{s}}\proj{k}$.
Since
\begin{equation}
\mathbf{1}_{\tau\left(P_{i}^{s}\right)}=\mathbf{1}_{\tau\left(\sum_{k\in S_{i}^{s}}\proj{k}\right)}=\mathbf{1}_{\bigcup_{k\in S_{i}^{s}}\tau\left(\proj{k}\right)}=\sum_{k\in S_{i}^{s}}\mathbf{1}_{\left\{ \ket{k}\right\} }\,,
\end{equation}
we have $X=\sum_{k=0}^{d-1}\lambda_{k}\mathbf{1}_{\ket{k}}$.\end{proof}

@@

\begin{proof}[Proof 1]Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\mu}\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one pair
of $\left(s_{0},i_{0}\right)$ such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$.
Therefore, 
\begin{equation}
\expval{\mathbf{O}}_{\mu}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\,.\label{eq:expectation-value-eigenvalue}
\end{equation}
\end{proof}

\begin{proof}[Proof 2]Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
we have
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,,
\end{equation}
where $X\left(\bar{\mu}^{-1}\left(\necess\right)\right)$ is an eigenvalue
of $\mathbf{O}$ by the definition of $X$.\end{proof}

@@

\begin{lemma}For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
and a sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $,
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
\end{lemma}

\begin{proof}Since $\left\{ \mathbf{O}_{j}\right\} $ is a sequence
of commuting observables, they can be diagonalized by a common orthonormal
basis\nb$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$. By theorem~\ref{thm:sub-event-space},
there is a commuting sub-event space\nb$\widehat{\events}$ with
$\widehat{\events}\subseteq\events$ and a bijection\nb$\tau:\widehat{\events}\rightarrow2^{\Omega}$
such that there is a CIVPM\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}_{\mathrm{D}}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$.

Let $\events'_{j}$ be the subspace of events induced by $\mathbf{O}_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\proj{k}$.
Clearly, $\events'_{j}\subseteq\widehat{\events}$. Therefore, restricting
$\tau$ on each $\events'_{j}$ gives a function\nb$\tau|_{\events'_{j}}:\events'_{j}\rightarrow2^{\Omega}$.
Then, we can follow lemma~\ref{lemma:observable2random-variable}
to induce random variables\nb$X_{j}=\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }$,
and have $\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\int X_{j}\rmd\bar{\mu}'$
by lemma~\ref{lemma:interval-expectation-value-between-classical-quantum}.
Therefore, 
\begin{eqnarray*}
 &  & \prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\prod_{j}\int X_{j}\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-product}}{=} & \int\prod_{j}X_{j}\rmd\bar{\mu}'=\int\prod_{j}\sum_{k=0}^{d-1}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'\\
 & = & \int\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\mathbf{1}_{\left\{ \ket{k}\right\} }\rmd\bar{\mu}'=\expval{\sum_{k=0}^{d-1}\prod_{j}\lambda_{j,k}\proj{k}}_{\bar{\mu}}\\
 & = & \expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\,.
\end{eqnarray*}
\end{proof}
